### 2018-06-11 Shiva Dissertation/chap2/realExperiment.tex
Shiva PhD dissertation

\begin{figure*}
\renewcommand{\figwid}{5.25cm}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[height=\figwid]{SetUp.pdf}%\put(1,75){A}
	\end{overpic}\begin{overpic}[height=5.5cm]{AllShapesR.pdf}%\put(-0,85){B}
	\end{overpic}\begin{overpic}[height=\figwid]{PotentialExp.pdf}%\put(-0,85){C}
	\end{overpic}
\end{center}
\caption{\label{fig:setup}
Hardware platform. At right are the shapes used for hardware experiments and a visualization of the potential field. }
\end{figure*}

@@

Even though kilobots are nonholonomic, they performed five successful runs manipulating a hexagonal object through an obstacle maze. Videos of these runs are in Extension 2. These hardware experiments represent the results of over 100 hours of trials.
Each trial used 100 kilobots. Trials two through five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the value iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central at \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std).

>>>>

\begin{figure*}
%\renewcommand{\figwid}{5.25cm}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.7\columnwidth]{SetUp.pdf}%\put(1,75){A}
	\end{overpic}\\
	\vspace{3em}
	\begin{overpic}[width=0.33\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
	\end{overpic}
	\begin{overpic}[width=0.6\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
	\end{overpic}
\end{center}
\caption{\label{fig:setup}
Hardware platform. At right are the shapes used for hardware experiments and a visualization of the potential field. }
\end{figure*}

@@

Even though kilobots are nonholonomic, they performed five successful runs manipulating a hexagonal object through an obstacle maze. Videos of these runs are in Extension 2. These hardware experiments represent the results of over 100 hours of trials.
Each trial used 100 kilobots. Trials two through five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the value iteration of Sec. \ref{subsec:objectpolicy} and the algorithm of Sec. \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central at \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std).

### 2018-06-11 Shiva Dissertation/chap2/relatedWork.tex
Shiva PhD dissertation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}\label{sec:RelatedWork}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Global-Control of Microrobots
%Block-Pushing and Compliant Manipulation
%Human-Swarm Interaction
%Microrobots can be produced in large numbers, but are generally controlled by global inputs.  This leads to challenges in sensing, 
This section describes global control challenges and reviews highlights of human-swarm interaction, block pushing, and compliant manipulation.

@@

This paper investigates global control of particles that have no onboard computation. This prevents us from applying controllers that require computation on the agents, as in \cite{milutinovic2006modeling,prorok2011multi,demir2015probabilistic}.
%\cite{milutinovic2006modeling} requires robots that can execute task primitives.  Our particles simply move in the direction of the global control unless they are stopped by an obstacle. 
%\cite{palmer2011hamiltonian} uses only Open-Loop control.  Our submission relies on state feedback 
%\cite{prorok2011multi} requires collective intelligence of a group of miniature robots
%\cite{demir2015probabilistic} requires robots that can individually decide when to actuate and when to remain anchored, can perform onboard computation (generate a random number, calculate its bin and the next bin). 
Another control paradigm is to construct robots with physical heterogeneity so that they respond differently to a global broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};  magnetic structures  with different cross-sections that can be independently steered by \cite{Floyd2011,Diller2013};  \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}. 
Similarly, our previous work focused on exploiting inhomogeneity between robots~\cite{Becker2012,Becker2012k}.  These control algorithms theoretically apply to any number of robots, even robotic continuums.
However, all these works never controlled more than twelve robots at a time because process noise cancels the differentiating effects of robot inhomogeneity.
%However, a consequence of the central limit theorem is that independent process noise cancels the differentiating effects of inhomogeneity for large numbers of robots. 
 We desire control algorithms that extend to many thousands of robots.
Limited position control was achieved by \cite{bretl2007control} and our previous work \cite{beckerIJRR2014}, but both used robots commanded in their local coordinate frame. Our new submission focuses on a more common paradigm: particles commanded in a global coordinate frame.

@@

\paragraph{Computation---calculating the control law}
In our previous work the controllers required at best a summation over all the robot states, see \cite{Becker2012k} and at worst a matrix inversion, see \cite{Becker2012}. 
These operations become intractable for large populations of robots. By focusing on \emph{human} control of large robot populations, we accentuate computational difficulties because the controllers are implemented by the unaided human operator. % We present an approach that, for many tasks, bypasses these problems due to large populations by allowing the user to command the entire population as a single unit.  For position control we cannot bypass this problem, but we provide an algorithm that scales linearly in the number of robots.

@@

  Most humans are able to, with practice, steer a swarm of robots controlled by a global input. Prior to our paper, no algorithm existed. Using human input to learn how to control a dynamic system is a line of research with a rich history \cite{argall2009, abbeel2010}. This paper exploits insights gained from \href{http://www.swarmcontrol.net}{\emph{SwarmControl.net}}, particularly the fact that having a swarm's mean and variance is sufficient for object manipulation through an obstacle field.

 A user interface enabling an operator to maneuver a swarm of robots through a cluttered workspace by specifying the bounding prism for the swarm and then translating or scaling this prism is designed in \cite{ayanian2014controlling}. Our paper shares the concept of a global control input, but our robots have no onboard computation and cannot track a virtual boundary.

Human \emph{fanout}, the number of robots a single human user could directly control is studied in \cite{Jr2004}.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, our paper indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with three levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in~\cite{odhner2014compliant} or silicone in~\cite{deimel2014novel}.  Our swarms tend to disperse and so to regroup them we require artificial forces like the variance control primitives in \S \ref{sec:VarianceControl}.

\subsection{Relationship to authors' prior work}
 This paper combines the content of two preliminary conference papers, extending their substance and providing full details in a single journal paper.  One paper covered the first three months of SwarmControl.net experiments~\cite{swarmcontrol2013}, and the second presented simulations of object manipulation~\cite{ShahrokhiIROS2015}. This paper presents three years of results from SwarmControl.net. For object manipulation, this paper presents robust new algorithms for manipulation, path planning, and obstacle avoidance, and a rich set of parameter sweeps over key variables. All hardware validation experiments are new.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}\label{sec:RelatedWork}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Global-Control of Microrobots
%Block-Pushing and Compliant Manipulation
%Human-Swarm Interaction
%Microrobots can be produced in large numbers, but are generally controlled by global inputs.  This leads to challenges in sensing, 
This section describes global control challenges and reviews highlights of human-swarm interaction, block pushing, and compliant manipulation.

@@

This dissertation investigates global control of particles that have no onboard computation. This prevents us from applying controllers that require computation on the agents, as in \cite{milutinovic2006modeling,prorok2011multi,demir2015probabilistic}.
%\cite{milutinovic2006modeling} requires robots that can execute task primitives.  Our particles simply move in the direction of the global control unless they are stopped by an obstacle. 
%\cite{palmer2011hamiltonian} uses only Open-Loop control.  Our submission relies on state feedback 
%\cite{prorok2011multi} requires collective intelligence of a group of miniature robots
%\cite{demir2015probabilistic} requires robots that can individually decide when to actuate and when to remain anchored, can perform onboard computation (generate a random number, calculate its bin and the next bin). 
Another control paradigm is to construct robots with physical heterogeneity so that they respond differently to a global broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};  magnetic structures  with different cross-sections that can be independently steered by \cite{Floyd2011,Diller2013};  \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}, similarly, exploiting inhomogeneity between robots~\cite{Becker2012,Becker2012k}.  These control algorithms theoretically apply to any number of robots, even robotic continuums.
However, all these works never controlled more than twelve robots at a time because process noise cancels the differentiating effects of robot inhomogeneity.
%However, a consequence of the central limit theorem is that independent process noise cancels the differentiating effects of inhomogeneity for large numbers of robots. 
 We desire control algorithms that extend to many thousands of robots.
Limited position control was achieved by \cite{bretl2007control} and \cite{beckerIJRR2014}, but both used robots commanded in their local coordinate frame. This chapter focuses on a more common paradigm: particles commanded in a global coordinate frame.

@@

\paragraph{Computation---calculating the control law}
There are controllers that require at best a summation over all the robot states, see \cite{Becker2012k} and at worst a matrix inversion, see \cite{Becker2012}. 
These operations become intractable for large populations of robots. By focusing on \emph{human} control of large robot populations, we accentuate computational difficulties because the controllers are implemented by the unaided human operator. % We present an approach that, for many tasks, bypasses these problems due to large populations by allowing the user to command the entire population as a single unit.  For position control we cannot bypass this problem, but we provide an algorithm that scales linearly in the number of robots.

@@

  Most humans are able to, with practice, steer a swarm of robots controlled by a global input. Prior to this work, no algorithm existed. Using human input to learn how to control a dynamic system is a line of research with a rich history \cite{argall2009, abbeel2010}. This chapter exploits insights gained from \href{http://www.swarmcontrol.net}{\emph{SwarmControl.net}}, particularly the fact that having a swarm's mean and variance is sufficient for object manipulation through an obstacle field.

 A user interface enabling an operator to maneuver a swarm of robots through a cluttered workspace by specifying the bounding prism for the swarm and then translating or scaling this prism is designed in \cite{ayanian2014controlling}. This chapter shares the concept of a global control input, but our robots have no onboard computation and cannot track a virtual boundary.

Human \emph{fanout}, the number of robots a single human user could directly control is studied in \cite{Jr2004}.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, this chapter indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with three levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in~\cite{odhner2014compliant} or silicone in~\cite{deimel2014novel}.  Our swarms tend to disperse and so to regroup them we require artificial forces like the variance control primitives in Sec. \ref{sec:VarianceControl}.

%\subsection{Relationship to authors' prior work}
% This paper combines the content of two preliminary conference papers, extending their substance and providing full details in a single journal paper.  One paper covered the first three months of SwarmControl.net experiments~\cite{swarmcontrol2013}, and the second presented simulations of object manipulation~\cite{ShahrokhiIROS2015}.

### 2018-06-11 Shiva Dissertation/chap3/Previous/intro.tex
Shiva PhD dissertation

\section{Introduction}\label{sec:Intro}
Micro-robots can be manufactured in large numbers.
Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection and 2) ex vivo to assemble structures in parallel. 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
 Future implementations require control techniques that can reliably exploit large populations despite significant under-actuation.

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{CoverPhoto.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:FirstImage}
Torque control of an object is essential for manipulating objects to their goal position  when there are narrow passageways and for aligning sensors, emitters, or other objects. 
This paper provides feedback control laws to apply torques and forces using a highly under-actuated system where all 
robots are controlled globally by the same input. 
(a) Simulation of robots exerting torque on a hinged ``door''.
(b) Simulation of swarm orientation manipulation.
(c) 97 hardware robots applying torque to an object. These robots have light sensors and are programmed to move toward the brightest light in the room.  This light is a shared control input that operates globally on the swarm. A full resolution video is available at:~\cite{ShahrokhiTorqueVideo}
}
\vspace{-1em}
\end{figure}

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\cite{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
Previous work proves that the mean position of a swarm is controllable and that, with an obstacle, the swarm's position variance orthogonal to rectangular boundary walls  is also controllable
(these are $\sigma_x^2$ and $\sigma_y^2$ for a workspace with axis-aligned walls). 
The usefulness of these techniques was demonstrated by several automatic controllers. One controller steered a swarm of robots to push a larger block through a 2D maze~\cite{ShahrokhiIROS2015}. 
We also showed methods to control a swarm's position covariance to enable the swarm to navigate through a workspaces with narrow corridors.  
However, object manipulation often also requires controlling torque on an object, for example changing the orientation of an object with a large aspect ratio to thread through narrow corridors.
Torque control  is also necessary for a variety of alignment tasks including retroreflectors, and targeted radiation therapy.

Accurate torque control is difficult.
A swarm with $n$ agents has $2n$ degrees of freedom.  
The swarm, when steered toward an object, begins interacting with the object at different times. 
The number of robots touching this object as a function of time is difficult to predict and often impossible to directly measure.
Stochastic effects make long-term prediction challenging.
Even when it is possible to predict which agents will hit the object first, as agents interact with the object, the swarm's configuration changes.
The challenge is not only limited to swarm-object interaction, but also to swarm-swarm interactions when the swarm self-collides  or is split into multiple components. 
As a result, the force the swarm will exert on the object is not easy to predict.
%Predicting the force a swarm exerts on an object requires knowing the location of every robot in contact with the object. 
This information is often hard to gather, because remote sensing of tiny particles is difficult.
Particles may be smaller than the minimum resolution of MRI, PET, and ultrasound, but these sensing modalities can still return aggregate data.
From this aggregate data,  some statistics---including mean and variance---are easy to obtain. 
Rather than design open-loop algorithms, this paper focuses on feedback control strategies using just two statistics of the swarm, the mean and variance of the swarm's position.

Fig. \ref{fig:FirstImage} illustrates the torque control using 97 kilobots, as well as two simulation snapshots of torque and orientation control.

>>>>

\section{Introduction}\label{sec:Intro}
%Micro-robots can be manufactured in large numbers.
%Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection and 2) ex vivo to assemble structures in parallel. 
% For each application, large numbers of micro robots are required  to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
% Future implementations require control techniques that can reliably exploit large populations despite significant under-actuation.

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{CoverPhoto.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:FirstImage}
Torque control of an object is essential for manipulating objects to their goal position  when there are narrow passageways and for aligning sensors, emitters, or other objects. 
This paper provides feedback control laws to apply torques and forces using a highly under-actuated system where all 
robots are controlled globally by the same input. 
(a) Simulation of robots exerting torque on a hinged ``door''.
(b) Simulation of swarm orientation manipulation.
(c) 97 hardware robots applying torque to an object. These robots have light sensors and are programmed to move toward the brightest light in the room.  This light is a shared control input that operates globally on the swarm. %A full resolution video is available at:~\cite{ShahrokhiTorqueVideo}
}
\vspace{-1em}
\end{figure}

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\cite{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
Previous chapter proves that the mean position of a swarm is controllable and that, with an obstacle, the swarm's position variance orthogonal to rectangular boundary walls  is also controllable
(these are $\sigma_x^2$ and $\sigma_y^2$ for a workspace with axis-aligned walls).

However, object manipulation often also requires controlling torque on an object, for example changing the orientation of an object with a large aspect ratio to thread through narrow corridors.
Torque control  is also necessary for a variety of alignment tasks including retroreflectors, and targeted radiation therapy.

With a single agent, torque control is straightforward: the agent simply maximizes the length of the movement arm to maximize torque. To make an agent push open a door, it should push on the edge furthest from the hinge. 
The optimal solution for a swarm of particles is not straightforward because they cannot all push at one position.

This paper focuses on optimizing control strategies using the swarm's position distribution. 
Fig. \ref{fig:FirstImage} illustrates the torque control using 97 kilobots, as well as two simulation snapshots of torque and orientation control.
This chapter first discusses the ways that we can control torque of an object in Section ~\ref{sec:theory}. Then it introduces algorithms for torque control in Section ~\ref{sec:simulation}. We show that algorithms work in Section ~\ref{sec:expResults} on up to 100 kilobots.
%Representative results are shown in Fig. \ref{fig:FirstImage}.

%Accurate torque control is difficult.
%A swarm with $n$ agents has $2n$ degrees of freedom.  
%The swarm, when steered toward an object, begins interacting with the object at different times. 
%The number of robots touching this object as a function of time is difficult to predict and often impossible to directly measure.
%Stochastic effects make long-term prediction challenging.
%Even when it is possible to predict which agents will hit the object first, as agents interact with the object, the swarm's configuration changes.
%The challenge is not only limited to swarm-object interaction, but also to swarm-swarm interactions when the swarm self-collides  or is split into multiple components. 
%As a result, the force the swarm will exert on the object is not easy to predict.
%%Predicting the force a swarm exerts on an object requires knowing the location of every robot in contact with the object. 
%This information is often hard to gather, because remote sensing of tiny particles is difficult.
%Particles may be smaller than the minimum resolution of MRI, PET, and ultrasound, but these sensing modalities can still return aggregate data.
%From this aggregate data,  some statistics---including mean and variance---are easy to obtain. 
%Rather than design open-loop algorithms, this paper focuses on feedback control strategies using just two statistics of the swarm, the mean and variance of the swarm's position.

### 2018-06-11 Shiva Dissertation/chap3/simulation.tex
Shiva PhD dissertation

\section{Simulation}\label{sec:simulation}
This section examines four main challenges for pose and torque control of an object, arranged in increasing difficulty.  Each task uses a PD controller that regulates the swarm's mean position,  as in \cite{ShahrokhiIROS2015}. The control input is the global force applied to each robot:
\begin{align}
u_x &= K_{p}(goal_x - \bar{x}) + K_{d}(0-\bar{v}_x) \nonumber\\
u_y &= K_{p}(goal_y  - \bar{y}) + K_{d}(0-\bar{v}_y)  \label{eq:PDcontrolPosition}
\end{align}
here $K_{p}$ is the proportional gain, and $K_{d}$ is the derivative gain.  
The swarm's average position is $[\bar{x},\bar{y}]^T$ and mean velocity is $[\bar{v}_x,\bar{v}_y]^T$.  
Each task uses a different algorithm to select the swarm's goal position $[goal_x,goal_y]^T$. The derivative gain $K_d$ limits overshoot.

\paragraph{Pure torque control} \label{sec:simulationPureTorque}
An object with a pivot point can rotate, but not translate. A door is an example.
 If there was only one robot touching the object, the robot should push at the point which maximizes the moment arm, at the extreme end of the object furthest from the pivot point.
The optimal pushing location provides the maximum force, because it maximizes  $r$ in \eqref{eq:torque}.
However, given a swarm of robots, maximizing $r$ is no longer the optimal solution.  
If the mean of the swarm hits the object at the extreme edge, half of the robots will miss the object and  the swarm will be split.
Because few robots remain,  the force is significantly decreased and torque is not maximized.
 In our simulation, the swarm applies torque until the swarm's mean position is beyond the object. Then the swarm will regather in a corner before returning to torque control, a time-consuming task. 
 The key parameter of interest for a hinged door of length $L$ is $C$, the position along the door where the mean of the swarm will push.  The goal position in ~\eqref{eq:TorqueControl} is set to:

\begin{align}\nonumber
goal_x &= O_x + C \cos(O_{\theta}) \\
goal_y &= O_y + C \sin(O_{\theta}),  \label{eq:TorqueControl}
\end{align}
$O_{\theta}$ = the orientation of the object's major axis, measured from the world $x$-axis.
 Fig. \ref{fig:LFig} illustrates how different values of $C$ result in different rates of turning. These simulations tested $C = \{1/2, 3/4, 5/8, 1\}L$. The fastest turning rates occurred with  $C =  5/8L$. Code is available at \cite{Shahrokhi16torque}.

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\columnwidth]{LFig.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:LFig}
Simulation results from a swarm applying force to a hinged door. 
The swarm mean is steered toward a point $C$ units along the object from the pivot point. The red dashed line indicates the times that the swarm was in variance control mode.
 Simulation used 144 robots of diameter $0.2$ m with a standard deviation of less than $1.5$ m and an object length of $6$ m.
}
\vspace{-1em}
\end{figure}

@@

 \begin{align}\nonumber
goal_x = O_x +  K_{orient}  (O_{\theta} - goal_\theta ) \cos(O_{\theta}) \\
goal_y = O_y +  K_{orient}  ( O_{\theta} -goal_\theta  ) \sin(O_{\theta})
\end{align}
Here $K_{orient}$ is a positive gain on the control input.

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\columnwidth]{Orientation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:OrientCont}
Plot demonstrating  orientation control of a rectangular object. The green line is the goal orientation. Other lines show different random starting position of the swarm. When the plot traces are constant the swarm is no longer pushing the object and instead is being regathered in a corner of the workspace until the variance is below a desired threshold. 
}
\vspace{-1em}
\end{figure}

@@

>>>>

\section{Simulation}\label{sec:simulation}
This section examines three challenges for torque control of an object, arranged in increasing difficulty.  Each task uses a PD controller that regulates the swarm's mean position,  as in \cite{ShahrokhiIROS2015}. The control input is the global force applied to each robot:
\begin{align}
u_x &= K_{p}(goal_x - \bar{x}) + K_{d}(0-\bar{v}_x) \nonumber\\
u_y &= K_{p}(goal_y  - \bar{y}) + K_{d}(0-\bar{v}_y)  \label{eq:PDcontrolPosition}
\end{align}
here $K_{p}$ is the proportional gain, and $K_{d}$ is the derivative gain.  
The swarm's average position is $[\bar{x},\bar{y}]^T$ and mean velocity is $[\bar{v}_x,\bar{v}_y]^T$.  
Each task uses a different algorithm to select the swarm's goal position $[goal_x,goal_y]^T$. The derivative gain $K_d$ limits overshoot.

\paragraph{Maximizing torque on a pivoted body} \label{sec:simulationPureTorque}
An object with a pivot point can rotate, but not translate. A door is an example.
 If there was only one robot touching the object, the robot should push at the point which maximizes the moment arm, at the extreme end of the object furthest from the pivot point.
% \begin{align}
%\tau = F \times (P - O )\label{eq:torque}
% = F \cdot (P - O )\label{eq:torque}
%\end{align}
The optimal pushing location provides the maximum force, because it maximizes the distance $r = \norm{P - O}$ in \eqref{eq:torque}.
However, given a swarm of robots, maximizing $r$ is no longer the optimal solution.  
If the mean of the swarm hits the object at the extreme edge, half of the robots will miss the object and  the swarm will be split.
Because few robots remain,  the force is significantly decreased and torque is not maximized.
 In our simulation, the swarm applies torque until the swarm's mean position is beyond the object. Then the swarm will regather in a corner before returning to torque control, a time-consuming task. 
 The key parameter of interest for a hinged door of length $L$ is $C$, the position along the door where the mean of the swarm will push.  The goal position in ~\eqref{eq:TorqueControl} is set to:

\begin{align}\nonumber
goal_x &= O_x + C \cos(O_{\theta}) \\
goal_y &= O_y + C \sin(O_{\theta}),  \label{eq:TorqueControl}
\end{align}
%\textcolor{red}{??The coordinate frames here are different from the rest of the paper}
$O_{\theta}$ = the orientation of the object's major axis, measured from the world $x$-axis.
 Fig. \ref{fig:LFig} illustrates how different values of $C$ result in different rates of turning. These simulations tested $C = \{1/2, 3/4, 5/8, 1\}L$. The fastest turning rates occurred with  $C =  5/8L$. Code is available at \cite{Shahrokhi16torque}.

%\textcolor{red}{??TODO: PUT THE NEW REAL SIMULATIONS HERE
%SIm 1: include  push at the optimal location
%}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=0.8\columnwidth]{LFig.pdf}
%\end{center}
%\vspace{-1em}
%\caption{\label{fig:LFig}
%Simulation results from a swarm applying force to a hinged door. 
%The swarm mean is steered toward a point $C$ units along the object from the pivot point. The red dashed line indicates the times that the swarm was in variance control mode.
% Simulation used 144 robots of diameter $0.2$ m with a standard deviation of less than $1.5$ m and an object length of $6$ m.
%}
%\vspace{-1em}
%\end{figure}

@@

 \begin{align}\nonumber
goal_x = O_x +  K_{\textrm{orient}}  (O_{\theta} - goal_\theta ) \cos(O_{\theta}) \\
goal_y = O_y +  K_{\textrm{orient}}   ( O_{\theta} -goal_\theta  ) \sin(O_{\theta})
\end{align}
Here $K_{orient}$ is a positive gain on the control input.

%\textcolor{red}{??TODO: PUT THE REAL SIMULATIONS HERE.}
%
%\begin{figure}
%\begin{center}
%	\includegraphics[width=0.8\columnwidth]{Orientation.pdf}
%\end{center}
%\vspace{-1em}
%\caption{\label{fig:OrientCont}
%Plot demonstrating  orientation control of a rectangular object. The green line is the goal orientation. Other lines show different random starting position of the swarm. When the plot traces are constant the swarm is no longer pushing the object and instead is being regathered in a corner of the workspace until the variance is below a desired threshold. 
%}
%\vspace{-1em}
%\end{figure}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\columnwidth]{LFig.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:LFig}
Simulation results from a swarm applying force to a hinged door. 
The swarm mean is steered toward a point $C$ units along the object from the pivot point. The red dashed line indicates the times that the swarm was in variance control mode.
% Simulation used 144 robots of diameter $0.2$ m with a standard deviation of less than $1.5$ m and an object length of $6$ m.
}
\vspace{-1em}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\columnwidth]{Orientation.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:OrientCont}
Plot demonstrating  orientation control of a rectangular object. The green line is the goal orientation. Other lines show different random starting position of the swarm.% When the plot traces are constant the swarm is no longer pushing the object and instead is being regathered in a corner of the workspace until the variance is below a desired threshold. 
}
\vspace{-1em}
\end{figure}
